---
title: "SUS"
output: html_notebook
---
```{r}
library(ggplot2)
library(ggpubr)
library(afex)
library(ggResidpanel)
library(psych)
library(emmeans)
library(rstatix)
library(gridExtra)
library(grid)

coloring = c("#ffbd67", "#f6dbb8","#94d8e0","#537b7f")
fontsize = 14
dodge = .75
```

#### Normality test

```{r}
df=read.csv('csv/sus.csv', sep=",")

# Subset the data
vr_as <- subset(df, conditions == "AS" & role == "VR")
vr_gs <- subset(df, conditions == "GS" & role == "VR")
vr_ms <- subset(df, conditions == "MS" & role == "VR")
vr_ns <- subset(df, conditions == "NS" & role == "VR")
ar_as <- subset(df, conditions == "AS" & role == "AR")
ar_gs <- subset(df, conditions == "GS" & role == "AR")
ar_ms <- subset(df, conditions == "MS" & role == "AR")
ar_ns <- subset(df, conditions == "NS" & role == "AR")

sh_vr_as <- shapiro.test(vr_as$sus_score)
sh_vr_gs <- shapiro.test(vr_gs$sus_score)
sh_vr_ms <- shapiro.test(vr_ms$sus_score)
sh_vr_ns <- shapiro.test(vr_ns$sus_score)
sh_ar_as <- shapiro.test(ar_as$sus_score)
sh_ar_gs <- shapiro.test(ar_gs$sus_score)
sh_ar_ms <- shapiro.test(ar_ms$sus_score)
sh_ar_ns <- shapiro.test(ar_ns$sus_score)

# Interpret normality based on p-values
interpret_normality <- function(p_value) {
  if (p_value > 0.05) {
    return("The data follows a normal distribution.")
  } else {
    return("The data does not follow a normal distribution.")
  }
}

# Print interpretation of normality for each subset
print(paste("vr_as:", interpret_normality(sh_vr_as$p.value), "W:", sh_vr_as$statistic, "p:", sh_vr_as$p.value))
print(paste("vr_gs:", interpret_normality(sh_vr_gs$p.value), "W:", sh_vr_gs$statistic, "p:", sh_vr_gs$p.value))
print(paste("vr_ms:", interpret_normality(sh_vr_ms$p.value), "W:", sh_vr_ms$statistic, "p:", sh_vr_ms$p.value))
print(paste("vr_ns:", interpret_normality(sh_vr_ns$p.value), "W:", sh_vr_ns$statistic, "p:", sh_vr_ns$p.value))
print(paste("ar_as:", interpret_normality(sh_ar_as$p.value), "W:", sh_ar_as$statistic, "p:", sh_ar_as$p.value))
print(paste("ar_gs:", interpret_normality(sh_ar_gs$p.value), "W:", sh_ar_gs$statistic, "p:", sh_ar_gs$p.value))
print(paste("ar_ms:", interpret_normality(sh_ar_ms$p.value), "W:", sh_ar_ms$statistic, "p:", sh_ar_ms$p.value))
print(paste("ar_ns:", interpret_normality(sh_ar_ns$p.value), "W:", sh_ar_ns$statistic, "p:", sh_ar_ns$p.value))


# balance 
table(df$role, df$conditions)


# qq plot, histogram
# qqnorm(vr_as$sus_score)
# qqline(vr_as$sus_score)
# qqnorm(vr_gs$sus_score)
# qqline(vr_gs$sus_score)
# qqnorm(vr_ms$sus_score)
# qqline(vr_ms$sus_score)
# qqnorm(vr_ns$sus_score)
# qqline(vr_ns$sus_score)
# qqnorm(ar_as$sus_score)
# qqline(ar_as$sus_score)
# qqnorm(ar_gs$sus_score)
# qqline(ar_gs$sus_score)
# qqnorm(ar_ms$sus_score)
# qqline(ar_ms$sus_score)
# qqnorm(ar_ns$sus_score)
# qqline(ar_ns$sus_score)


hist(df$sus_score)
```


#### Quick box-plot

```{r}
df=read.csv('csv/sus.csv', sep=",")
condition_order <- c("NS", "MS", "GS", "AS")
df$conditions <- factor(df$conditions, levels = condition_order)
boxplot(sus_score ~ conditions, data = df, 
        main = "Boxplot Example",
        xlab = "Category",
        ylab = "Value")
# Calculate mean for each category
means <- aggregate(sus_score ~ conditions, data = df, mean)

# Add mean points
points(x = as.numeric(means$conditions), y = means$sus_score, pch = 4)
```

SUS data is normally distributed, one-way ANOVA to compare the means of the SUS scores between the different conditions. 

```{r}
model <- aov_4(sus_score ~ conditions + (conditions|participant), type= 3, data = df)
summary(model)

print('# Perform repeated measures ANOVA with nice()')
modelnice <- nice(model, intercept = TRUE, correction = "GG")

print(modelnice) # ges: generalized eta-squared, measure of effect size indicating the proportion of variance explained by the independent variable.

emmip(model, ~conditions, CIs = TRUE)
```
```{r}
posthoc <- emmeans(model, specs = pairwise ~ conditions, model = "multivariate", adjust = "tukey")
posthoc$emmeans
posthoc$contrasts
```

```{r}
model <- aov_4(sus_score ~ conditions*vr_ar + (conditions|participant), type= 3, data = df)
summary(model)

print('# Perform repeated measures ANOVA with nice()')
modelnice <- nice(model, intercept = TRUE, correction = "GG")
# ges: generalized eta-squared, measure of effect size indicating the proportion of variance explained by the independent variable.
print(modelnice)

print('# Posthoc')
posthoc <- emmeans(model, specs = pairwise ~ conditions*vr_ar, model = "multivariate", adjust = "tukey") # tukey/bonferroni
posthoc$emmeans
posthoc$contrasts


emmip(model, vr_ar~conditions, CIs = TRUE)
```

```{r}
model <- aov_4(sus_score ~ conditions*vr_ar + (conditions|participant), type= 3, data = df)
summary(model)

print('# Perform repeated measures ANOVA with nice()')
modelnice <- nice(model, intercept = TRUE, correction = "GG")
print(modelnice)  # ges: generalized eta-squared, measure of effect size indicating the proportion of variance explained by the independent variable.

print('# Posthoc')
posthoc <- emmeans(model, specs = pairwise ~ conditions*vr_ar, model = "multivariate", adjust = "tukey") # tukey/bonferroni
posthoc$emmeans
posthoc$contrasts


emmip(model, vr_ar~conditions, CIs = TRUE)
```


Extract residual/predicted values
```{r}
new_data <- fitted(model, append = TRUE)
residual_data <- residuals(model, append = TRUE)
new_data$.residuals <- residual_data$.residuals
head(new_data, 20)

describe(new_data$.residuals, type=1)

shapiro.test(new_data$.residuals)

resid_auxpanel(residuals=new_data$.residuals, predicted=new_data$.fitted, smoother = TRUE, qqbands=TRUE, 
               plots=c('resid', 'qq', 'index', 'hist'))
```

Based on the ANOVA table, the p-value (0.327) is greater than the significance level of 0.05, suggesting that there is no significant evidence to reject the null hypothesis. This indicates that there are no significant differences observed between the conditions in terms of the SUS scores.


```{r}
df=read.csv('csv/sus.csv', sep=",")
condition_order <- c("NS", "MS", "GS", "AS")
df$conditions <- factor(df$conditions, levels = condition_order)

# stat.test <- df %>% 
#   t_test(sus_score~conditions, p.adjust.method = 'bonferroni') %>%
#   add_significance("p") %>%
#   add_xy_position(x = "conditions")

tukey <- df %>% 
  tukey_hsd(sus_score ~ conditions) %>% 
  add_significance() %>% 
  add_xy_position()

bxp <- ggplot(df, aes(x = conditions, y = sus_score)) + 
  stat_boxplot(aes(fill = conditions), geom = "errorbar", width = 0.2, position = position_dodge(dodge)) +
  geom_boxplot(aes(fill = conditions), width = dodge/2, coef = 0, outlier.alpha = 0, show.legend = F) +
  stat_summary(aes(fill = conditions), fun.y = mean, 
               geom= "point", shape = 4, size = 5, colour= "black", 
               position = position_dodge(width = dodge)) +
  stat_summary(aes(fill = conditions), fun = median,
               geom = "crossbar", fatten = .1, width = .4*dodge, color = "black",
               position = position_dodge(width = dodge)) +
  labs(x = NULL, y = NULL) + 
  theme_bw()

bxp + 
  # stat_pvalue_manual(stat.test, label = 'p.signif', hide.ns = TRUE, tip.length = 0.02) + 
  stat_pvalue_manual(tukey, hide.ns = T) +
  scale_fill_manual(name= "conditions", values = coloring) +
  scale_color_manual(name = "conditions", values = coloring) +
  scale_y_continuous(minor_breaks = seq(0, 115, 20), breaks = seq(0, 115, by=20), limits=c(0, 115)) +
  theme(
    axis.line = element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    axis.text.x = element_text(color="black", size=fontsize),
    axis.text.y = element_text(color="black", size=fontsize),
    text = element_text(size=fontsize),
    strip.background = element_blank(),
    plot.background = element_blank(),
    plot.margin = unit(c(0.005, .025, 0, 0), "null"),
    panel.border = element_blank(),
    panel.spacing = unit(c(0, 0, 0, 0), "null"),
    legend.key = element_blank(),
    legend.key.size = unit(1, "cm"),
    legend.key.height = unit(1.5, 'cm'), 
    legend.key.width = unit(1, 'cm'), 
    legend.position="bottom",
    legend.direction = "horizontal",
    legend.justification = c("center", "top"),
    legend.title=element_blank(),
    legend.text=element_text(size=fontsize),
    legend.box.just = "right",
    legend.box.background = element_blank()
  ) + 
  guides(fill = guide_legend(override.aes = list(color = "transparent")))
# saving the final figure
ggsave("out/sus.pdf", width = 6, height = 4, dpi = 1000)

```


```{r}
df=read.csv('csv/sus.csv', sep=",")
condition_order <- c("NS", "MS", "GS", "AS")
df$conditions <- factor(df$conditions, levels = condition_order)

# Create boxplot using ggplot
p <- ggplot(df, aes(x = conditions, y = sus_score)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot(aes(fill = conditions)) +
  stat_summary(fun.y = mean, geom="point", shape = 4, size = 3) +  
  labs(x = NULL, y = NULL) + 
  theme_bw()

# Add significance bars
p <- p + 
  stat_compare_means(
    comparisons = list(
      c("NS", "MS"), c("MS", "GS"), c("NS", "GS"), 
      c("GS", "AS"), c("NS", "AS"), c("MS", "AS")
    ),
    method = "t.test",
    exact = FALSE,
    p.adjust.method = "bonferroni",
    label = "p.signif",
    size = 3,
    label.x.npc = "left",
    label.y.npc = "top"
  )
p + 
  scale_fill_manual(name= "conditions", values = coloring) +
  theme(
    axis.line = element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    axis.text.x = element_text(color="black", size=fontsize),
    axis.text.y = element_text(color="black", size=fontsize),
    text = element_text(size=fontsize),
    strip.background = element_blank(),
    plot.background = element_blank(),
    plot.margin = unit(c(0.005, .025, 0, 0), "null"),
    panel.border = element_blank(),
    panel.spacing = unit(c(0, 0, 0, 0), "null"),
    legend.position="bottom",
    legend.direction = "horizontal",
    legend.justification = c("center", "top"),
    legend.title=element_blank(),
    legend.text=element_text(size=fontsize),
    legend.box.just = "right",
    legend.box.background = element_blank()
  )
```
VR--AR

```{r}
custom_boxplot <- function(df, dodge, fontsize, coloring, tag) {
  ggplot(df, aes(x = conditions, y = sus_score)) + 
    stat_boxplot(aes(fill = conditions), geom = "errorbar", width = 0.1, position = position_dodge(dodge/4)) +
    geom_boxplot(aes(fill = conditions), width = dodge/4, coef = 0, outlier.alpha = 0, show.legend = F) +
    stat_summary(aes(fill = conditions), fun.y = mean, 
                 geom= "point", shape = 4, size = 3, colour= "black", 
                 position = position_dodge(width = dodge)) +
    stat_summary(aes(fill = conditions), fun = median,
                 geom = "crossbar", fatten = .1, width = dodge/4, color = "black",
                 position = position_dodge(width = dodge/4)) +
    labs(x = NULL, y = NULL) + 
    theme_bw() + 
    stat_pvalue_manual(tukey, hide.ns = T) +
    scale_fill_manual(name= "conditions", values = coloring) +
    scale_color_manual(name = "conditions", values = coloring) +
    scale_y_continuous(minor_breaks = seq(0, 115, 20), breaks = seq(0, 115, by=20), limits=c(0, 115)) +
    ylim(0, 100) +
    labs(tag = tag) +
    annotation_custom(grid::linesGrob(y = c(0,0), gp = grid::gpar(lwd=3))) +
    theme(
      axis.line = element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      axis.text.x = element_text(color="black", size=fontsize),
      axis.text.y = element_text(color="black", size=fontsize),
      text = element_text(size=fontsize),
      strip.background = element_blank(),
      plot.background = element_blank(),
      plot.margin = unit(c(0.005, .045, 0, 0), "null"),
      panel.border = element_blank(),
      plot.tag = element_text(angle = 90, vjust = 1, size=fontsize),
      plot.tag.position = c(1, .5),
      panel.spacing = unit(c(0, 0, 0, 0), "null"),
      legend.key = element_blank(),
      legend.key.size = unit(.5, "cm"),
      legend.key.height = unit(1, 'cm'), 
      legend.key.width = unit(.75, 'cm'), 
      legend.position="bottom",
      legend.direction = "horizontal",
      legend.justification = c("center", "top"),
      legend.title=element_blank(),
      legend.text=element_text(size=fontsize, margin = margin(r = 5)),
      legend.margin = margin(0, 0, 0, 0),
      legend.spacing.x = unit(0.1, "cm"),
      legend.spacing.y = unit(0, "cm"),
      legend.box.just = "right",
      legend.box.background = element_blank()
    ) 
}

df=read.csv('csv/sus.csv', sep=",")
condition_order <- c("NS", "MS", "GS", "AS")
df$conditions <- factor(df$conditions, levels = condition_order)

df_ar <- df[df$role == 'AR', ]
df_vr <- df[df$role == 'VR', ]


# stat.test <- df %>% 
#   t_test(sus_score~conditions, p.adjust.method = 'bonferroni') %>%
#   add_significance("p") %>%
#   add_xy_position(x = "conditions")

tukey <- df %>% 
  tukey_hsd(sus_score ~ conditions) %>% 
  add_significance() %>% 
  add_xy_position()

bxp_vr <- custom_boxplot(df_vr, dodge, fontsize, coloring, "remote user") + 
  theme(
    axis.text.x = element_blank(),
    legend.position="none",
    plot.margin = unit(c(0.005, .045, 0.05, 0), "null"),
    plot.tag.position = c(1, .5),
  ) 

bxp_ar <- custom_boxplot(df_ar, dodge, fontsize, coloring, "local user") + 
    theme(
      plot.tag.position = c(1, .7),
    ) +
    guides(fill = guide_legend(override.aes = list(color = "transparent")))


final_plot <- arrangeGrob(bxp_vr, bxp_ar, nrow = 2, heights = c(.4, .6))
grid.arrange(final_plot)
# saving the final figure
ggsave("out/sus.pdf", final_plot, width = 6, height = 4, dpi = 1000)
```